---
title: "sequential_analysis_complete_02.28.2020"
author: "Jonas Schöne"
date: "28 February 2020"
output: html_document
---

d: full dataset
d_mem: subset of memory task
deq: subset of sequential task
dl: Long format dataset for analysis of hypothesis 1 (Main Effect)

###Library/Cleaning the Environment/ggplot default settings/Getting the Data/Get the Data/Prepare Variables for Aggregation

```{r}
if(!require(Rmisc)) {install.packages("Rmisc"); require(Rmisc)}
if(!require(tidyverse)) {install.packages("tidyverse"); require(tidyverse)}
if(!require(lme4)) {install.packages("lme4"); require(lme4)}
if(!require(car)) {install.packages("car"); require(car)}
if(!require(jsonlite)) {install.packages("jsonlite"); require(jsonlite)}
if(!require(lmerTest)) {install.packages("lmerTest"); require(lmerTest)}

rm(list = ls()) #Cleaning the R Environment, since the datasets are pretty big and can slow down the PC 

theme_set(theme_bw()) #simple black and white design

#setwd("D:/Desktop/Oxford/amplification_project/analysis/sequential_study2_block/") #path to the json data files
#setwd("D:/Desktop/Oxford/amplification_project/analysis/data_memory_blockwise/") #old unsuccessful memory task
#path =  "data_old/" #pilot with to many single faces
#path =  "data_old/test_trials" #for test trials


d <- read.csv("data/sequential_study1_Jun2020_just_amplification_different_sequences.csv")

#############################################################################################################
################
################                            CLEANING DATA/SUBSETTING                           ##############
################
#############################################################################################################

# Subsetting the Trial Types
#First subsetting the squential task


d$estimation <- as.integer(d$estimation)
test <- d %>% 
  dplyr::group_by(participant_id) %>% 
  dplyr::summarise(estimation_diff = mean(estimation_diff, na.rm=TRUE))


Participant_Overview_Sequential <- d %>% 
   dplyr::group_by(participant_id) %>% 
   dplyr::summarise(estimation = mean(estimation, na.rm=TRUE), finished_trials = max(trial) , rt_seq = mean(rt)) %>% 
  ungroup()

 
exclusion_cases_seq <- Participant_Overview_Sequential %>% 
   filter(estimation < 10 | estimation > 40)  

d <- subset(d, !(participant_id %in% exclusion_cases_seq$participant_id))

# Creating a long format to test general Amplification variable

dl = d%>%
  select( participant_id, trial, faceIdentity, fixationTime,estimation,face_mean, valence)%>%
  gather(ratingType, ratingValue , -participant_id, -trial, -faceIdentity, - fixationTime, -valence)


#rm (attention_check, df_total,exclusion_cases,exclusion_table, json_data)

#Functions 
lineGraph = function(data, outcome,group1,time,title, xtitle,ytitle){
  dfc=summarySE(data, measurevar=outcome,
                groupvars=c(group1,time), na.rm = T)
  print(dfc)
  dfc$high = dfc[,4]+dfc[,6]
  dfc$low = dfc[,4]-dfc[,6]
  pd <- position_dodge(0)
  ggplot(dfc,aes_string(x=time, y=outcome ,fill = group1, colour =group1))+
    geom_errorbar(aes(ymin=low, ymax=high), width=.1)+
    geom_line( aes_string(linetype= group1, group=group1),size = .5)+
    #facet_wrap(as.formula(paste("~", group1)),nrow=2)+
    geom_point()+
    theme_bw()+
    theme(plot.title = element_text(hjust=0.5,size = rel(1.5)),
          axis.title.y = element_text(face="bold",  size=14),
          axis.text.x  = element_text( vjust=0.5, size=18),
          axis.text.y  = element_text( vjust=0.5, size=12),
          axis.title.x = element_text( vjust=0.5, size=18)) +
    labs(title = title,
          x = xtitle, 
          y = ytitle)

}


length(unique(d$participant_id))

```

### Descriptives Sequence

```{r}
des = d %>%
  group_by(participant_id, valence) %>%
  summarize(meanDif = mean(estimation_diff),
            sdDif = sd (estimation_diff)) ;des

hist(d$estimation_diff, main = paste("Histogram of Estimation Difference"))
mean(d$estimation_diff)

hist(d$face_mean, main = paste("Histogram of actual Face Emotions"))
hist(d$estimation, main = paste("Histogram of Estimations"))

d$count <- 1


```

###Analysis Main Effect

```{r}
dl$ratingType = factor(dl$ratingType)

meanCondition = dl %>%
  group_by(ratingType) %>%
  summarize(ratingValueM = mean (ratingValue, na.rm =T))

dl$ratingType = relevel(dl$ratingType , "face_mean")

r = lmer(ratingValue ~ ratingType  +(1|participant_id), dl);summary(r)

dfc <- summarySE(dl, measurevar="ratingValue", groupvars=c("ratingType", "valence"), na.rm = T)

g = ggplot(dfc,aes(x=as.factor(ratingType), y = ratingValue, fill = valence))+
  geom_bar(position=position_dodge(), width = 0.5,stat="identity", colour="black" )+
  geom_errorbar(aes(ymin=ratingValue-ci, ymax=ratingValue+ci), width=.1,position=position_dodge(.5))+
  theme_bw()+
  theme(plot.title = element_text(size = rel(1.4), hjust = 0.5,),
        axis.title.y = element_text(face="bold",  size=14),
        axis.text.x  = element_text( vjust=0.5, size=18),
        axis.text.y  = element_text( vjust=0.5, size=12),
        axis.title.x = element_blank()) +
    scale_fill_grey()+
    #facet_wrap(~id)+
    #geom_hline(yintercept = 0.5,linetype="dashed", color = "red")+
    labs(title = "", x = "",y = "difference(estimation-real)");g


r = lmer(ratingValue ~ ratingType*valence +(1|participant_id)+(1|faceIdentity), dl);summary(r)

dfc <- summarySE(dl, measurevar="ratingValue", groupvars=c("ratingType"), na.rm = T)

g = ggplot(dfc,aes(x=as.factor(ratingType), y=ratingValue))+
  geom_bar(position=position_dodge(), width = 0.5,stat="identity", colour="black" )+
  geom_errorbar(aes(ymin=ratingValue-ci, ymax=ratingValue+ci), width=.1,position=position_dodge(.5))+
  theme_bw()+
  theme(plot.title = element_text(size = rel(1.4), hjust = 0.5,),
        axis.title.y = element_text(face="bold",  size=14),
        axis.text.x  = element_text( vjust=0.5, size=18),
        axis.text.y  = element_text( vjust=0.5, size=12),
        axis.title.x = element_blank()) +
    scale_fill_grey()+
    #facet_wrap(~id)+
    #geom_hline(yintercept = 0.5,linetype="dashed", color = "red")+
    labs(title = "", x = "",y = "difference(estimation-real)");g

#################### Hypothesis 1: Main Effect * FixationTime

r = lmer(ratingValue ~ ratingType*fixationTime +(1|participant_id)+(1|faceIdentity), dl);summary(r)
```

```{r}
d$valence=relevel(d$valence, "positive")

r = lmer (estimation_diff ~ valence+ scale(face_number) + (1|participant_id),d); summary(r)


dfc <- summarySE(d, measurevar="estimation_diff", groupvars=c("valence","participant_id"), na.rm = T)

g = ggplot(dfc,aes(x=as.factor(valence), y=estimation_diff))+
  geom_bar(position=position_dodge(), width = 0.5,stat="identity", colour="black" )+
  geom_errorbar(aes(ymin=estimation_diff-ci, ymax=estimation_diff+ci), width=.1,position=position_dodge(.5))+
  theme_bw()+
  theme(plot.title = element_text(size = rel(1.4), hjust = 0.5,),
        axis.title.y = element_text(face="bold",  size=14),
        axis.text.x  = element_text( vjust=0.5, size=18),
        axis.text.y  = element_text( vjust=0.5, size=12),
        axis.title.x = element_blank()) +
    scale_fill_grey()+
    facet_wrap(~participant_id)+
    #geom_hline(yintercept = 0.5,linetype="dashed", color = "red")+
    labs(title = "", x = "",y = "difference(estimation-real)");g
```



### Primacy and Recency Effect
```{r}
r = lmer (estimation_diff ~  first_face  + (1|participant_id), d); summary(r)

ggplot(d, aes(x = last_face, y = estimation_diff, colour = valence), filter(d,face_number > 2))+ # recency effect visualisation
  geom_smooth() 

ggplot(d, aes(x = first_face, y = estimation_diff, colour = valence), filter(d,face_number > 2))+ # primacy effect visualisation
  geom_smooth() 

##### First Face Over Trials

ff <- d %>% 
  group_by(trial) %>%
  do(ff_coeff=fixef(lmer(estimation_diff ~  first_face  + (1|faceIdentity), data=.))[[2]])

ff$ff_coeff <- unlist(ff$ff_coeff)

r = lmer (estimation_diff ~ trial * first_face  + (1|participant_id) + (1|faceIdentity), d); summary(r)

ggplot(ff, aes(x = trial, y = ff_coeff))+ # primacy effect visualisation
  geom_smooth() 

### First Face Face Number

ff <- d %>% 
  group_by(face_number) %>%
  do(ff_coeff=fixef(lmer(estimation_diff ~  first_face  + (1|faceIdentity), data=.))[[2]])

ff$ff_coeff <- unlist(ff$ff_coeff)

r = lmer (estimation_diff ~ first_face * face_number  + (1|participant_id) + (1|faceIdentity), d); summary(r)

ggplot(ff, aes(x = face_number, y = ff_coeff))+ # primacy effect visualisation
  geom_smooth() 
```


### Trial Development

```{r}

ggplot(d, aes(x = trial, y = estimation_diff, colour = valence))+
  geom_smooth(method = lm) 

lineGraph(d,"estimation_diff","valence","trial",title="Ratings Over Time","trial","ratings")

```

### Amits suggestions from email 04/03/2020

```{r}

# 1b.) Correlation between positive and negative amplification

# by participant
dtest = d %>%
  group_by(participant_id, valence) %>%
  summarize(meanDif = mean(estimation_diff),
            sdDif = sd (estimation_diff)) %>% 
  ungroup()

dtest <- spread(dtest, valence, meanDif)

dcor <- dtest %>% 
  dplyr::group_by(participant_id) %>% 
  dplyr::summarise(negative = last(na.omit(negative)), positive = last(na.omit(positive))) %>%
  ungroup()


cor.test (dcor$negative,dcor$positive)

ggplot(dcor, aes(x = negative, y = positive))+ 
  geom_point()+
  geom_smooth(method = lm) 

linearMod_participants <- lm(positive ~ negative, data=dcor)  # build linear regression model on full data
summary(linearMod_participants)

# by trial

dtest = d %>%
  group_by(trial, valence) %>%
  summarize(meanDif = mean(estimation_diff),
            sdDif = sd (estimation_diff)) %>% 
  ungroup()

dtest <- spread(dtest, valence, meanDif)

dcor <- dtest %>% 
  dplyr::group_by( trial) %>% 
  dplyr::summarise(negative = last(na.omit(negative)), positive = last(na.omit(positive))) %>%
  ungroup()

ggplot(dcor, aes(x = negative, y = positive))+ 
  geom_smooth(method = lm) 

linearMod_trials <- lm(positive ~ negative, data=dcor)  # build linear regression model on full data
summary(linearMod_trials)


```




### 2 hypothesis: Face Number

```{r , amplification}

## testing consistency of effect at different stages of experiment ## 

# Add grouping variable !!!



d %>%
  group_by(valence)%>%
  do(r=print(summary(lmer(estimation_diff ~ face_number +(1|participant_id),data=.))))

r = lmer (estimation_diff ~ face_number * valence + (1|participant_id), filter(d,face_number >= 2)); summary(r)


## Plotting Result

coef=d %>%
  group_by(valence) %>% 
  do(r=print(summary(lmer(estimation_diff~ face_number+(1|participant_id) , data = .))))%>%
  mutate(intercept = r$coefficients[1],
         face_number = r$coefficients[2])

ggplot(d, aes(x = face_number, y = estimation_diff, colour = valence)) +
  geom_point(size=3) +
  geom_abline(slope = coef$face_number[1], intercept = coef$intercept[1], colour ="red")+
  geom_abline(slope = coef$face_number[2], intercept = coef$intercept[2], colour ="blue")

ggplot(d, aes(x = face_number, y = estimation_diff, colour = valence))+ #Comparison of positive and negative emotion
  geom_smooth(method = "lm") +
  geom_hline(yintercept= 0, linetype="dashed", color = "red")+
  scale_x_continuous(breaks = round(seq(min(d$face_number), max(d$estimation_diff), by = 1),1))

```

#### Order Analysis

```{r}

d_order <- read.csv("data/sequential_study1_Jun2020_just_amplification_different_sequences_NOT_AGGREGATED.csv")

d_order <- subset(d_order, !(participant_id %in% exclusion_cases_seq$participant_id))

r = lmer (estimation_diff ~ order_of_face * stimulus + (1|participant_id), d_order); summary(r)

ggplot(d_order, aes(x = stimulus, y = estimation_diff), d_order)+ # , colour = valence
  geom_smooth(se=F) +
  facet_wrap( ~as.factor(order_of_face))

d_order <- d_order %>% 
  group_by(order_of_face) %>% 
  do(print(summary(lmer (estimation_diff ~ stimulus + (1|participant_id), data=.))))

dpl <- d_order %>% 
  dplyr::group_by(order_of_face) %>% 
  do(Slope=fixef(lmer(estimation_diff ~ stimulus + (1|participant_id) + (1|faceIdentity),data=.))[[2]]) %>% 
  ungroup()

dpl$Slope <- unlist(dpl$Slope)

ggplot(dpl,aes(x=as.factor(order_of_face), y= Slope))+
  geom_bar(position=position_dodge(), width = 0.5,stat="identity", colour="black" )+
  theme_bw()+
  scale_y_continuous(trans = "reverse")+
  theme(plot.title = element_text(size = rel(1.4), hjust = 0.5,),
        axis.title.y = element_text(face="bold",  size=14),
        axis.text.x  = element_text( vjust=0.5, size=18),
        axis.text.y  = element_text( vjust=0.5, size=12),
        axis.title.x = element_blank()) +
    scale_fill_grey()
```




#### Power Analysis

```{r}
library(simr)
```


### Amity Power Analysis with smaller subset

```{r}
#1. You take the trials of 8 from the first 50 - I can't imagine we have more than 2 in the first 25 and that's not enough (but you should do this anlysis as well).

dl_test = d%>% #Filtering the 8 sequences and if needed the first 25 cases
  filter(face_number == 8 & trial < 50) %>% 
  select( participant_id, trial, faceIdentity, estimation,face_mean)%>%
  gather(ratingType, ratingValue , -participant_id, -trial, -faceIdentity)

dl_test$count <- 1 # to count how often people saw 8 faces

test <- dl_test %>% # this is the table of how often people saw 8 faces
  group_by(participant_id) %>% 
  summarise(trialnumber = sum(count))

#2. You calculate the effect.

PowerModel = lmer(ratingValue ~ ratingType +(1|participant_id), dl_test);summary(PowerModel)

powerSim(PowerModel, nsim=100)

powerCurve(PowerModel, nsim = 10, within = "ratingType")

#3. You extend it to trials to see how much you need.

PowerModelExt = extend(PowerModel, within = "ratingType", n = 350)
pc <-  powerCurve(PowerModelExt, nsim = 10, within = "ratingType") #80% at around 150 - 200 trials
pc
plot(pc)
powerSim(PowerModelExt, nsim=100)


# 4. You extend it to people to see how much you need. 

PowerModelExtP = extend(PowerModelExt, along = "participant_id", n = 100)
pc <-  powerCurve(PowerModelExtP, nsim = 10, along = "participant_id")
powerSim(PowerModelExtP, nsim=100)
pc
plot(pc)

PowerModelExt = extend(PowerModel, along = "participant_id", n = 100)
pc <-  powerCurve(PowerModelExt, nsim = 10, along = "participant_id")
powerSim(PowerModelExt, nsim=100)
pc
plot(pc)

```
